The Occurrence of Earth-Like Planets Around Other Stars

### 2014-11-25 paper/kepler-selection.tex
New plots showing background density and detection efficiency, etc, plus captions

\author{Will M. Farr$^{1}$, Chris Aldridge$^{1}$, Kirsty Stroud$^{1}$ \& Ilya Mandel$^{1}$}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{eta-earth}
  \caption{\label{fig:eta-earth} \textbf{The posterior on $\etaearth \equiv \left. \frac{dN_\mathrm{pl}}{d\ln P \,d \ln
      R} \right|_{P = 1\mathrm{yr}, R=1\REarth}$
      accounting for selection effects and false positives.}  Vertical lines
    indicate the 90\% credible range.  We find $\etaearth = \earange$.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{npl}
  \caption{\label{fig:npl} \textbf{The posterior on $\Rpl$, the number of planets per star.}  Vertical lines
    indicate the 90\% credible range.  We find $\Rpl =
    \rplrange$.}
\end{figure}

>>>>

\author{Will M. Farr$^{1}$, Ilya Mandel$^{1}$, Chris Aldridge$^{1}$ \& Kirsty Stroud$^{1}$}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{pars}
  \caption{\label{fig:eta-earth} \textbf{Posteriors on $\etaearth$ and
      $Rpl$ accounting for selection effects and false-positive
      detections.}  (Top) The inferred posterior density on $\etaearth
    = dN/d\ln P \, d\ln R \left( 1\, \textnormal{yr}, R_\oplus
    \right)$.  Vertical lines indicate the 90\% credible range.  We
    find $\etaearth = \earange$.  (Bottom) The inferred posterior on
    $\Rpl$, the number of planets per star with $P \lesssim 3
    \mathrm{yr}$ and $R \gtrsim 0.2 \REarth$.  Vertical lines indicate
    the 90\% credible range.  We find $\Rpl = \rplrange$.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{bg}
  \caption{\label{fig:npl} \textbf{Inferred detection probability and
      density of background contamination.} (Top) The inferred
    detection probability versus signal-to-noise ratio (see
    Eq.\ \eqref{eq:pdetect}) from our parameterised model of selection
    effects.  The solid line is the posterior median detection
    probability and the shading gives the 90\% credible posterior
    interval.  Our inferred detection probability is in rough
    agreement with the measurements of detection efficiency in
    Refs.\ \cite{Borucki2011,Batalha2013}.  (Bottom) The number
    density of false-positive candidate signals, $d\Nbg/d\ln P \, d\ln
    R$ (see Eq.\ \eqref{eq:background-rate}).  The density is highest
    at large candidate period and radius, consistent with the dominant
    source of contamination being background eclipsing
    binaries\cite{Fressin2013}.  Overall, our model finds $\fposrange$
    of the candidates are false-positive background signals,
    consistent with the analysis in Ref.\ \cite{Fressin2013}.}
\end{figure}
